Job Demands-Resources model components through the lens of O*NET classifications

### 2022-11-18 Submission.Rmd
Updating the introduction
graphs

Of greatest interest here are statements taken from O\*NET ["activity" and "context" classifications](https://www.O\*NETonline.org/find/descriptor/result/4.A.1.b.3) (e.g., items related to information input, interacting with others, physical work conditions, structural job characteristics). One of the first and basic questions is whether or not the categorical examples of "resources" and "demands" described in the Job Demands-Resources Theory [@demerouti2001job], for example, are generally deemed resources or demands as we objectively define them. The next logical question surrounds how "universal" such ratings are. For instance, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance. A second study extends the findings from Study 1 to a potentially key moderator - job categories/classifications, examining whether ratings of resources, challenge- and hindrance demands differ by job classification.

@@

# Study 2

@@

```{r scale-level-graphs, eval = FALSE}
#this is a placeholder for the scale level faceted graph found in plotscript_practice script file. 
```

>>>>

Of greatest interest here are statements taken from O\*NET ["activity" and "context" classifications](https://www.O\*NETonline.org/find/descriptor/result/4.A.1.b.3) (e.g., items related to information input, interacting with others, physical work conditions, structural job characteristics). One of the first and basic questions is whether or not the categorical examples of "resources" and "demands" described in the Job Demands-Resources Theory [@demerouti2001job], for example, are generally deemed resources or demands as we objectively define them. The next logical question surrounds how "universal" such ratings are. For instance, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance.

@@

@@

```{r scalelevelgraphs, fig.cap="Average characteristic rating grouped by literature-implicated categorizations."}

#this is a placeholder for the scale level faceted graph found in plotscript_practice script file. 
#Open the Submission .rmd
#Run chunks up to the source recodes chunk (named, `generalrecodes`), and then use the data object
#to create the ggplot

library(ggplot2)
library(plyr)
library(dplyr)

#Demands (resources ratings)
#These are the literature-based categories, and composites - means - of Onet item ratings
data$resources_workpressure <- rowMeans(subset(data, select = c(item120, item121)), na.rm = TRUE)
data$resources_phyworkload_wkover <- rowMeans(subset(data, select = c(item122, item137, item138,
                                                                      item139, item141, item142,
                                                                      item143)), na.rm = TRUE)
data$resources_timepressure <- rowMeans(subset(data, select = c(item125, item126)), na.rm = TRUE)
data$resources_recipientcontact <- rowMeans(subset(data, select = c(item149, item154, item157, 
                                                                    item160, item186, item188, 
                                                                    item192, item197, item200, 
                                                                    item201, item151)), na.rm = TRUE)
data$resources_phyenvironment <- rowMeans(subset(data, select = c(item128, item129,	item130, item132,
                                                                  item133,item134,	item136,	item144,	item146,
                                                                  item147,	item148,	item177,	item180,
                                                                  item182,	item181,	item183)), na.rm = TRUE)
data$resources_emotionaldemands <- rowMeans(subset(data, select = c(item150, item155, item199)), na.rm = TRUE)

#Demands (challenge ratings)
#These are the literature-based categories, and composites - means - of Onet item ratings
data$challenge_workpressure <- rowMeans(subset(data, select = c(item290, item291)), na.rm = TRUE)
data$challenge_phyworkload_wkover <- rowMeans(subset(data, select = c(item292, item307, 
                                                                      item309, item310,	item312,
                                                                      item313,	item314)), na.rm = TRUE)
data$challenge_timepressure <- rowMeans(subset(data, select = c(item295, item296)), na.rm = TRUE)
data$challenge_recipientcontact <- rowMeans(subset(data, select = c(item319, item324, item327,
                                                                    item330, item356, item358,
                                                                    item362, item367, item370,
                                                                    item371, item321)), na.rm = TRUE)
data$challenge_phyenvironment <- rowMeans(subset(data, select = c(item298, item299, item300, item302,
                                                                  item303, item304,item306, item315, item316,
                                                                  item317, item318, item347, item350,
                                                                  item352, item351, item353)), na.rm = TRUE)
data$challenge_emotionaldemands <- rowMeans(subset(data, select = c(item320, item325, item369)), na.rm = TRUE)

#Demands (hindrance ratings)
#These are the literature-based categories, and composites - means - of Onet item ratings
data$hindrance_workpressure <- rowMeans(subset(data, select = c(item205, item206)), na.rm = TRUE)
data$hindrance_phyworkload_wkover <- rowMeans(subset(data, select = c(item207, item222,item223,
                                                                      item224, item226, item227,
                                                                      item228)), na.rm = TRUE)
data$hindrance_timepressure <- rowMeans(subset(data, select = c(item210, item211)), na.rm = TRUE)
data$hindrance_recipientcontact <- rowMeans(subset(data, select = c(item233, item238, item241, 
                                                                    item244, item271, item273,
                                                                    item277,	item282,	item285,
                                                                    item286, item235)), na.rm = TRUE)
data$hindrance_phyenvironment <- rowMeans(subset(data, select = c(item213, item214, item215, item217,
                                                                  item218, item219, item221, item229,
                                                                  item230,	item231,	item232,	
                                                                  item262, item265, item267, item266,
                                                                  item286)), na.rm = TRUE)
data$hindrance_emotionaldemands <- rowMeans(subset(data, select = c(item234, item239, item284)), na.rm = TRUE)

#Resources (resource ratings)
#These are the literature-based categories, and composites - means - of Onet item ratings
data$resource_jobcontrol <- rowMeans(subset(data, select = c(item124, item127)), na.rm = TRUE)
data$resource_participation <- rowMeans(subset(data, select = c(item158, item159,
                                                                item172,	item174, item175,
                                                                item189, item193, item202)), na.rm = TRUE)
data$resource_teamcohesion <- rowMeans(subset(data, select = c(item161, item190, item191)), na.rm = TRUE)
data$resource_autonomy <- rowMeans(subset(data, select = c(item118, item172)), na.rm = TRUE)

#Resources (challenge ratings)
#These are the literature-based categories, and composites - means - of Onet item ratings
data$challenge_jobcontrol <- rowMeans(subset(data, select = c(item294, item297)), na.rm = TRUE)
data$challenge_participation <- rowMeans(subset(data, select = c(item328, item329, item342,
                                                                 item344, item345, item359, item363,
                                                                 item372)), na.rm = TRUE)
data$challenge_teamcohesion <- rowMeans(subset(data, select = c(item331, item360, item361)), na.rm = TRUE)
data$challenge_autonomy <- rowMeans(subset(data, select = c(item288, item342)), na.rm = TRUE)

#Resources (hindrance ratings)
#These are the literature-based categories, and composites - means - of Onet item ratings
data$hindrance_jobcontrol <- rowMeans(subset(data, select = c(item209, item212)), na.rm = TRUE)
data$hindrance_participation <- rowMeans(subset(data, select = c(item242, item243, item257,	item259,
                                                                 item260,	item274,	item278,
                                                                 item287)), na.rm = TRUE)
data$hindrance_teamcohesion <- rowMeans(subset(data, select = c(item245, item275, item276)), na.rm = TRUE)
data$hindrance_autonomy <- rowMeans(subset(data, select = c(item203, item257)), na.rm = TRUE)

#check the autonomy variables
summary(data$hindrance_autonomy)
summary(data$challenge_autonomy)
summary(data$resource_autonomy)
library(tidyr)

toplot <- gather(data, scale, value, resources_workpressure:hindrance_autonomy, factor_key=TRUE)

library(stringr)
toplot$type <- str_sub(toplot$scale, 1,6)
toplot$onet <- str_sub(toplot$scale, 10,-1)

toplot$type[toplot$type == "challe"] <- "Challenge"
toplot$type[toplot$type == "hindra"] <- "Hindrance"
toplot$type[toplot$type == "resour"] <- "Resource"       ## change `onet` later if want to keep graphs

toplot$onet[toplot$onet == "teamcohesion"] <- "Team Cohesion"       
toplot$onet[toplot$onet == "_teamcohesion"] <- "Team Cohesion"  
toplot$onet[toplot$onet == "participation"] <- "Participation"       
toplot$onet[toplot$onet == "_participation"] <- "Participation"  
toplot$onet[toplot$onet == "jobcontrol"] <- "Job Control"       
toplot$onet[toplot$onet == "_jobcontrol"] <- "Job Control"  
toplot$onet[toplot$onet == "autonomy"] <- "Autonomy"       
toplot$onet[toplot$onet == "_autonomy"] <- "Autonomy"

toplot$onet[toplot$onet == "_emotionaldemands"] <- "Emotional Demands"          ## added 11/18/22 (Hudson)  
toplot$onet[toplot$onet == "_phyenvironment"] <- "Physical Environment"  
toplot$onet[toplot$onet == "_phyworkload_wkover"] <- "Overwork"  
toplot$onet[toplot$onet == "_recipientcontact"] <- "Recipient Contact"  
toplot$onet[toplot$onet == "_timepressure"] <- "Time Pressure"  
toplot$onet[toplot$onet == "_workpressure"] <- "Work Pressure"

toplotgg <- ddply(toplot, c("type", "onet"), summarise, average = mean(value, na.rm=TRUE))

table(toplot$onet)

## Probably want to change this to a facet: 3 different grids grouped by literature-described 1) resource, 2) hindrances, and 3) challenge

toplotgg$facet <- c("Lit Resource", "Lit Demand", "Lit Resource", "Lit Demand", "Lit Resource", "Lit Demand", "Lit Demand", "Lit Resource", "Lit Demand", "Lit Demand",
                    "Lit Resource", "Lit Demand", "Lit Resource", "Lit Demand", "Lit Resource", "Lit Demand", "Lit Demand", "Lit Resource", "Lit Demand", "Lit Demand",
                    "Lit Resource", "Lit Demand", "Lit Resource", "Lit Demand", "Lit Resource", "Lit Demand", "Lit Demand", "Lit Resource", "Lit Demand", "Lit Demand")

##############################################################
##############################################################
################    Plots

demandsplot <- filter(toplotgg, facet == "Lit Demand")
resourcesplot <- filter(toplotgg, facet == "Lit Resource")

## Demands

demandsplot$onet <- factor(demandsplot$onet, levels=c("Work Pressure", "Recipient Contact", "Emotional Demands", "Time Pressure", "Physical Environment", "Overwork"))

a <- ggplot(data=demandsplot, aes(x=onet, y=average, fill=type)) + 
  geom_bar(stat="identity", position=position_dodge(), color="black") + coord_flip(ylim=c(1,5)) + scale_fill_manual(values=c("#000000","#cccccc","#ffffff")) +
  scale_x_discrete(labels=function(x){sub("\\s", "\n", x)}) +
  theme(legend.title=element_blank(), legend.position="none",  panel.border = element_rect(colour = "black", fill=NA, size=.5), axis.title.x = element_blank(), axis.title.y = element_blank())

## Resources

resourcesplot$onet <- factor(resourcesplot$onet, levels=c("Team Cohesion", "Autonomy", "Participation", "Job Control"))

b <- ggplot(data=resourcesplot, aes(x=onet, y=average, fill=type)) + 
  geom_bar(stat="identity", position=position_dodge(), color="black") + coord_flip(ylim=c(1,5)) + scale_fill_manual(values=c("#000000","#cccccc","#ffffff")) +
  scale_x_discrete(labels=function(x){sub("\\s", "\n", x)}) +
  theme(legend.title=element_blank(), legend.position="bottom",  panel.border = element_rect(colour = "black", fill=NA, size=.5), axis.title.x = element_blank(), axis.title.y = element_blank())

################################################################
################################################################
################################################################

library("gridExtra")
grid.arrange(a, b, ncol = 2, nrow = 1)

see Figure \@ref(fig:scalelevelgraphs)
